---
title: "Homework 1: TidyTuesday - Many Penguins Analysis"
author: "Joseph Saputra"
date: "2026-09-15"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
```

## Background & Research Question

In this assignment, I explored simple body measurements from the **Many Penguins** dataset (AVONET database) [https://opentraits.org/datasets/avonet.html data source](https://opentraits.org/datasets/avonet.html).

**Research Question:** Do penguins with longer legs also have longer wings, and which penguin genus has the longest wings overall?

## Data Loading

```{r}
library(tidyverse)

# Load dataset directly from GitHub
penguins <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-07-14/many_penguins.csv")
```

## Plot 1: Leg Length vs. Wing Length

We use a scatterplot (geom_point) to check if leg length (tarsus.length) is related to wing length (wing.length).

```{r}

ggplot(penguins, aes(x = tarsus.length, y = wing.length)) +
  geom_point(color = "red", size = 2.5, alpha = 0.8) +
  labs(
    title = "Penguin Leg Length vs. Wing Length",
    subtitle = "Penguins with longer legs generally have longer wings",
    x = "Tarsus (Leg) Length (mm)",
    y = "Wing Length (mm)",
    caption = "Source data taken from: AVONET"
  ) +
  theme_minimal()
```

## Plot 2: Wing Length by Genus

We use a boxplot (geom_boxplot) to compare wing lengths across different penguin genera.

```{r}
ggplot(penguins, aes(x = genus, y = wing.length, fill = genus)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  labs(
    title = "Wing Length Distribution Across Penguin Genera",
    subtitle = "Aptenodytes penguins have the longest wings of any genus",
    x = "Penguin Genus",
    y = "Wing Length (mm)",
    caption = "Source data taken from: AVONET"
  ) +
  theme_minimal() 


```

## Main Takeaways

**Positive Trend:** Leg length and wing length show a straightforward positive relationship—larger body frames mean longer limbs.

**Genus Variation:** Aptenodytes penguins stand out with noticeably larger average wing measurements than all other genera.
