---
title: "Homework 1: TidyTuesday - Cappuccino Index Analysis"
author: "Joseph Saputra"
date: "2026-09-15"
format: html
editor: visual
---

## Background & Research Question

In this assignment, I explored James Hoffmann's Cappuccino Index dataset to see how long a barista must work to buy a small cappuccino.

**Research Question:** Which countries have the most affordable cappuccino relative to barista wages, and is there a direct relationship between barista wages and cappuccino prices?

## Data Loading & Cleaning

First of all, let us load and read the data as well as wrangling it together

```{r}
library(tidyverse)

# Load datasets
cafe <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-09-08/cafe.csv")
cappuccino_index <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-09-08/cappuccino_index.csv")

# Clean non-breaking spaces in country names ( I was experimenting on how to do it )
cafe$country <- gsub("\u00a0", " ", cafe$country)
cappuccino_index$country <- gsub("\u00a0", " ", cappuccino_index$country)
```

## Plot 1: Most Affordable Countries for Baristas

I use a geom_col to look at the top 10 countries where baristas need to work the fewest minutes to afford a cappuccino (filtering for countries with at least 3 cafes sampled).

```{r}
top_affordable <- cappuccino_index %>%
  filter(n >= 3) %>%
  slice_min(index, n = 10)

ggplot(top_affordable, aes(x = reorder(country, index), y = index)) +
  geom_col(fill = "brown", alpha = 0.85) +
  coord_flip() +
  labs(
    title = "Where Can Baristas Afford Coffee the Fastest?",
    subtitle = "Minutes of work required to buy one small cappuccino (Countries with > 3 cafes)",
    x = "Country",
    y = "Work Time Required (Minutes)",
    caption = "Source: TidyTuesday Cappuccino Index"
  ) +
  theme_minimal()

```

## Plot 2: Barista Wage vs. Cappuccino Price

Then I use geom_point to test if higher hourly wages mean higher coffee prices in cafes worldwide.

```{r}
ggplot(cafe, aes(x = hourly_wage_gbp, y = price_gbp)) +
  geom_point(color = "green", alpha = 0.6, size = 2.5) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen") +
  labs(
    title = "Barista Hourly Wage vs. Cappuccino Price",
    subtitle = "Linear regression line confirms higher wages correspond with higher cappuccino prices",
    x = "Hourly Wage (£)",
    y = "Cappuccino Price (£)",
    caption = "Source: TidyTuesday Cappuccino Index"
  ) +
  theme_minimal()
```

## Conclusion

- **Affordability Differences:** Baristas in countries with higher minimum wages only need to work a few minutes to afford a cappuccino.
- **Positive Relationship:** As expected, cafes paying higher hourly wages in £ also tend to charge more for a cappuccino in GBP.
- **Regression Trend Line:** The linear regression line displays a clear upward slope, confirming a positive overall correlation between barista pay and drink prices across global cafes.
